---
title: "CDPH Course Analytics"
author: "David Connell and Michelle Ruiz"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(kableExtra)
```



# R/RStudio Fundamentals, on-demand ongoing offering

## Enrollment

1. Download entire enrollment CSV from [catalog analytics](https://cdph.catalog.instructure.com/new_analytics/listings)
2. Rename CSV file "enrollment_export.csv"
3. Move CSV file into course-analytics folder

```{r import-data, include=FALSE}
enrollment_export <- read_csv("enrollments_export.csv")
```

```{r include=FALSE}
r_fund <- filter(enrollment_export, `Listing Name` == "R and RStudio Fundamentals")
```

**`r dim(r_fund)[1]`** total participants enrolled in R/RStudio Fundamentals as of `r Sys.Date()`

```{r include=FALSE}
one_week_ago <- today()-7
r_fund_week <- filter(r_fund, `Created At` > one_week_ago)
```

**`r dim(r_fund_week)[1]`** participants enrolled in R/RStudio Fundamentals since `r one_week_ago`

## Certificates

1. Go to [certifier.io](https://certifier.io/), go to "Credentials", select all, export
2. Rename CSV file "certificates.csv"
3. Move CSV file into course-analytics folder

```{r include=FALSE}
certificates <- read_csv("certificates.csv")
r_fund_certs <- filter(certificates, `Group name` == "R and R Studio Fundamentals")
r_fund_certs_week <- filter(r_fund_certs, `Issued on` > one_week_ago)
```

**`r dim(r_fund_certs)[1]`** received a certificate of completion for R/RStudio Fundamentals as of `r Sys.Date()` and **`r dim(r_fund_certs_week)[1]`** received it since `r one_week_ago`

\newpage

## Viewership


```{r include=FALSE}
r_grades <- read_csv("Grades-R_and_R_Studio_Foundamentals.csv")
```


```{r echo=FALSE}
r_grades %>% 
    summarize_if(is.numeric, sum, na.rm=TRUE) %>%
    kable(caption = "Views per video")
```


```{r echo=FALSE}
r_grades %>%
    mutate(sum = rowSums(across(where(is.numeric)), na.rm = TRUE)) %>%
    pull(sum) %>%
    table() %>%
    kable(caption = "Number of videos watched by participants",
          col.names = c("Videos completed","Frequency"),
          align = "c")
```


# Data Visualization, August-December 2024 offering

1. Download **entire gradebook** from canvas as CSV
2. Rename CSV file to remove date
3. Move CSV file into course-analytics folder 

## Enrollment

```{r include=FALSE}
viz <- filter(enrollment_export, `Listing Name` == "Data Visualization for Public Health")
```

**`r dim(viz)[1]`** total participants enrolled in Data Visualization as of `r Sys.Date()`

```{r include=FALSE}
viz_week <- filter(viz, `Created At` > one_week_ago)
```

**`r dim(viz_week)[1]`** participants enrolled in Data Visualization since `r one_week_ago`

## Viewership

```{r include=FALSE}
viz_grades <- read_csv("Grades-Data_Visualization_for_Public_Health.csv")
viz_video_names <- names(viz_grades[seq(from = 6, to = 24)])
```

```{r include=FALSE}
df_long <- viz_grades %>%
    filter(Student != "Points Possible", Student != "Student, Test") %>% # remove "points possible row from gradebook and the test student
    select(-(2:5)) %>% # remove unneeded data columns
    select(-(21:39)) %>% # remove grade columns that aren't for individual videos
    pivot_longer(cols = 2:20,
                 names_to = "Video",  # column with video names
                 values_to = "Watched") %>% # column with the value 1 for "watched"
    filter(Watched == 1) # keep only rows where the video was watched

# put videos in sequential order
viz_video_levels <- rev(c("Introduction (1647)",
                          "dplyr basics (1650)",
                          "Beyond the Bar Graph (1643)",
                          "Introduction to Data Visualization Using Excel (1644)",
                          "Data Transformations (1651)",
                          "Deep Dive: ggplot syntax and bar charts (1645)",
                          "Color theory and Palettes (1653)",
                          "Continuous Data (1654)",
                          "Creating Scatter Plots and Bubble Charts with Excel (1685)",
                          "Scatterplots and Line Chart Basics (1655)",
                          "Line Plots and Scatterplots (Continuous Data) (1669)",
                          "Bubble and Line Charts (1676)",
                          "Accessibility and Ethics Comprehension Check in (1677)",
                          "Creating Publication Ready Graphics (1678)",
                          "Mapping Methods (1702)",
                          "Choropleth maps (1703)",
                          "Spatial Data Visualization on RStudio Exercise (1722)",
                          "Leaflet Guided R Practice (1716)",
                          "Creating graphics for difference audience (1706)"))

# viz_video_weeks <- 

# summarize the data to count viewership
video_count <- df_long %>%
    count(Video) %>%
    mutate(Video_fac = factor(Video,
                              levels = viz_video_levels,
                              ordered = TRUE))
```


```{r echo=FALSE}
title <- paste0("Views of course videos as of ", today())

# bar chart
ggplot(video_count, aes(y = Video_fac, x = n)) +
    geom_bar(stat = "identity", fill = "#2a6d9e") +
    labs(y = "Video title", x = "View count", 
         title = title) +
    theme_minimal()
```




How many people have watched each of the videos in the course?

Since there are many videos for this course, this code be summarized in a
graphic where on the x axis you have video number (organized
chronologically) and the y axis is the completion rate or the number of
people who have completed the video. If there are many videos each
week some indicator of the corresponding week can be added to the plot.
o When the plot is made, denote the current date (when the data was pulled) and
add a dashed vertical line to the plot in between videos that occur before and
after that date.

# Causal Inference, July-September 2024 offering



## Enrollment

```{r include=FALSE}
causal <- filter(enrollment_export, `Listing Name` == "Introduction to Causal Inference for Public Health Professionals")
```

**`r dim(causal)[1]`** total participants enrolled in Introduction to Causal Inference for Public Health Professionals as of `r Sys.Date()`

```{r include=FALSE}
causal_week <- filter(causal, `Created At` > one_week_ago)
```

**`r dim(causal_week)[1]`** participants enrolled in Introduction to Causal Inference for Public Health Professionals since `r one_week_ago`

## Certificates

```{r include=FALSE}
causal_certs <- filter(certificates,
                       `Group name` == "Causal Trailblazer Tier 1" |
                           `Group name` == "Causal Navigator Tier 2" |
                           `Group name` == "Causal Explorer Tier 3" )
causal_certs_week <- filter(causal_certs, `Issued on` > one_week_ago)
```


```{r echo=FALSE}
title2 <- paste0("Total certificates granted as of ", today())

causal_certs %>% 
    group_by(`Group name`) %>%
    summarize(Certificates = n()) %>%
    kable(caption = title2,
          col.names = c("Tier","Number of certificates"))
```

```{r echo=FALSE}
title3 <- paste0("Certificates granted since ", today()-7)

causal_certs %>%
    filter(`Issued on` > today()-7) %>%
    group_by(`Group name`) %>%
    summarize(Certificates = n()) %>%
    kable(caption = title3,
          col.names = c("Tier","Number of certificates"))
```

**`r dim(r_fund_certs)[1]`** received a certificate of completion for R/RStudio Fundamentals as of `r Sys.Date()` and **`r dim(r_fund_certs_week)[1]`** received it since `r one_week_ago`

## Viewership

```{r include=FALSE}
# causal_grades <- read_csv("Grades-Causal_Inference.csv",
#                           col_types = "cnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnnn")
#     
# str(causal_grades)
# 
causal_grades <- read_csv("Grade-Causal_Transformed.csv")
```
```{r include=FALSE}
causal_grades_long <- causal_grades %>%
    pivot_longer(cols = 2:36,
                 names_to = "Video",  # column with video names
                 values_to = "Watched") %>% # column with the value 1 for "watched"
    filter(Watched == 1) # keep only rows where the video was watched
```


```{r include=FALSE}
causual_video_names <- rev(c("Lecture1b", "Lecture1d", "Lecture2a","Lecture2b", "Lecture2c", "Lecture2d","Lecture2e", "Lecture2f", "Lecture3a", "Lecture4a", "Lecture4b", "Lecture4c", "Lecture4d", "Lecture5a", "Lecture5c", "Lecture5e", "Lecture5d",  "Lecture7a", "Lecture7d", "Lecture8a", "Lecture8b", "Lecture8c", "Lecture9a", "Lecture9b", "Lecture9c", "Lecture9d", "Lecture9e", "Lecture10a", "Lecture10b", "Lecture10c", "Lecture10d", "Lecture11a", "Lecture11b", "Lecture11c", "Lecture11d"))

#  summarize the data to count viewership
causal_video_count <- causal_grades_long %>%
    count(Video) %>%
    mutate(Video_fac = factor(Video,
                              levels = causual_video_names,
                              ordered = TRUE))
```


```{r echo=FALSE}
title4 <- paste0("Views of course videos as of ", today())

# bar chart
ggplot(causal_video_count, aes(y = Video_fac, x = n)) +
    geom_bar(stat = "identity", fill = "#2a6d9e") +
    labs(y = "Video title", x = "View count", 
         title = title4) +
    theme_minimal()
```
