---
title: "CDPH Course Analytics"
author: "David Connell and Michelle Ruiz"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```



# R/RStudio Fundamentals, on-demand ongoing offering

## Enrollment

1. Download entire enrollment CSV from [catalog analytics](https://cdph.catalog.instructure.com/new_analytics/listings)
2. Rename CSV file "enrollment_export.csv"
3. Move CSV file into course-analytics folder

```{r import-data, include=FALSE}
enrollment_export <- read_csv("enrollments_export.csv")
```

```{r include=FALSE}
r_fund <- filter(enrollment_export, `Listing Name` == "R and RStudio Fundamentals")
```

`r dim(r_fund)[1]` total participants enrolled in R/RStudio Fundamentals as of `r Sys.Date()`

```{r include=FALSE}
one_week_ago <- today()-7
r_fund_week <- filter(r_fund, `Created At` > one_week_ago)
```

`r dim(r_fund_week)[1]` participants enrolled in R/RStudio Fundamentals since `r one_week_ago`

## Certificates

TODO: add instructions for getting CSV from certificate generator website

1. Go to [certifier.io](), go to "Credentials" and select all, export
2. Rename CSV file "certificates.csv"
3. Move CSV file into course-analytics folder

```{r include=FALSE}
certificates <- read_csv("certificates.csv")
r_fund_certs <- filter(certificates, `Group name` == "R and R Studio Fundamentals")
r_fund_certs_week <- filter(r_fund_certs, `Issued on` > one_week_ago)
```

**`r dim(r_fund_certs)[1]`** received a certificate of completion for R/RStudio Fundamentals as of `r Sys.Date()` and **`r dim(r_fund_certs_week)[1]`** received it since `r one_week_ago`

## Viewership

list of videos and how many have seen each video total

how many have seen all 5
seen 4
seen 3
seen less than 3




# Data Visualization, August-December 2024 offering

1. Download **entire gradebook** from canvas as CSV
2. Rename CSV file to remove date
3. Move CSV file into course-analytics folder 

## Enrollment

```{r include=FALSE}
viz <- filter(enrollment_export, `Listing Name` == "Data Visualization for Public Health")
```

`r dim(viz)[1]` total participants enrolled in Data Visualization as of `r Sys.Date()`

```{r include=FALSE}
viz_week <- filter(viz, `Created At` > one_week_ago)
```

`r dim(viz_week)[1]` participants enrolled in Data Visualization since `r one_week_ago`

## Viewership

```{r}
viz_grades <- read_csv("Grades-Data_Visualization_for_Public_Health.csv")
```

```{r}
viz_video_names <- names(viz_grades[seq(from = 6, to = 24)])
viz_video_views <- tibble(video_names = viz_video_names,
                          views = NA)


dim(filter(viz_grades, `Introduction (1647)` == 1))[1]


temp <- viz_grades %>%
    group_by(across(6:24)) %>%
    summarise(n = n())
```

```{r}
# Assuming your data frame is named df
# First, let’s convert the data frame from wide to long format
df_long <- viz_grades %>%
    select(-(2:5)) %>%
    select(-(21:39)) %>%
  pivot_longer(
    cols = 2:20,
    names_to = "Video",  # This will be the new column with video names
    values_to = "Watched" # This will be the new column with the values 1 or 0
  ) %>%
    filter(Watched == 1) # Keep only rows where the video was watched





# Now, we can summarize the data to count viewership
video_count <- df_long %>%
  count(Video) %>%
  arrange(desc(n)) # Optional: Arrange in descending order of counts

video_count_new <- video_count %>%
    mutate(order = case_when(
        Video == "Introduction (1647)" ~ 1,
        Video == "Color theory and Palettes (1653)" ~ 3)) %>%
    arrange(order)



# Now let’s create a bar chart with ggplot2
ggplot(video_count, aes(y = Video, x = n)) +
  geom_bar(stat = "identity") +
  labs(y = "Video", x = "View Count")
```




How many people have watched each of the videos in the course?

Since there are many videos for this course, this code be summarized in a
graphic where on the x axis you have video number (organized
chronologically) and the y axis is the completion rate or the number of
people who have completed the video. If there are many videos each
week some indicator of the corresponding week can be added to the plot.
o When the plot is made, denote the current date (when the data was pulled) and
add a dashed vertical line to the plot in between videos that occur before and
after that date.

# Causal Inference, July-September 2024 offering



## Enrollment

```{r include=FALSE}
causal <- filter(enrollment_export, `Listing Name` == "Introduction to Causal Inference for Public Health Professionals")
```

`r dim(causal)[1]` total participants enrolled in Introduction to Causal Inference for Public Health Professionals as of `r Sys.Date()`

```{r include=FALSE}
causal_week <- filter(causal, `Created At` > one_week_ago)
```

`r dim(causal_week)[1]` participants enrolled in Introduction to Causal Inference for Public Health Professionals since `r one_week_ago`

## Viewership

